Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-27 article.tex
Appendix: ready to be proofread
Fix

\section*{Acknowledgments}
A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is
recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
Office.

@@

\section{Particularities of the ``Full method''}
\label{app:optimized}

@@

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering the argument in Section \ref{sec:results}, the additional
gain margin of this approach compared to the undirected method is extremely
limited.

@@

\begin{table}[ht]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
 without directivity & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
  with directivity  & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
\hline
\end{tabular}
\caption{Performance on \textit{normal-1,2,3,4} of the ``Full Method'' with and without the directivity heuristic.}
\label{tab:directivity}
\end{table}

@@

\begin{table}[h]
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   &  &  &  & & &\\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3* & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   &  &  &  & & &\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3* & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
\end{tabular}
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\end{table}

>>>>

\paragraph{Acknowledgments}
A. Joly and G. Louppe are research fellows of the FNRS, Belgium.  A. Sutera is
recipient of a FRIA fellowship of FRS-FNRS, Belgium. This work is supported by
PASCAL2 and the IUAP DYSCO, initiated by the Belgian State, Science Policy
Office.

@@

\section{Particularities of ``Full method''}
\label{app:optimized}

@@

Since partial correlation statistics is a symmetric measure and the connectome
is a directed graph, it should be rewarding to detect the edge orientation. In
this section, we will present a heuristic trying to retrieve directivity.
However, considering results in Section \ref{sec:results}, we expect that the
additionnal gain margin should be extremely limited.

@@

\begin{table}[ht]\label{tab:comparison}
%\caption{Evaluation of different methods on the four \textit{normal} datasets\label{tab:comparison}}
\centering
\small
\begin{tabular}{| l | c c c c | c c c c |}
\hline
& \multicolumn{4}{c|}{AUROC} & \multicolumn{4}{c|}{AUPRC} \\
\textit{Full method} $\backslash$ \textit{normal-} & \textit{1} & \textit{2} & \textit{3} & \textit{4} & \textit{1} & \textit{2} & \textit{3} & \textit{4} \\
\hline
\hline
 without directivity & 0.943 & 0.942 & 0.942 & 0.939 & 0.403 & 0.404 & 0.398 & 0.388  \\
  with directivity  & \textbf{0.944} & \textbf{0.943} & 0.942 & \textbf{0.940} & \textbf{0.404} & \textbf{0.405} & \textbf{0.399} & \textbf{0.389}\\
\hline
\end{tabular}
\caption{Performance on \textit{normal-1,2,3,4} of ``Full Method'' with and without the directivity heuristic.}
\label{tab:directivity}
\end{table}

@@

\begin{table}[h]
\centering
\small
\begin{tabular}{| l | c c c c c c |}
\hline
& \multicolumn{6}{c|}{AUROC}\\
\textit{Method} $\backslash$ \textit{normal-} & \textit{lowcon} & \textit{highcon} & \textit{lowcc} & \textit{highcc} & \textit{3-highrate} & \textit{4-lownoise} \\
\hline
\hline
Averaging     & 0.947 & 0.943 & 0.920 & 0.942 & 0.959 & 0.934 \\
Full method   &  &  &  & & &\\
PC & 0.782 & 0.920 &  0.846 & 0.897  & 0.898  & 0.873 \\
GTE & 0.846 & 0.905 & 0.848 & 0.899 & 0.905 & 0.879\\
GENIE3 & 0.781 &  0.922 & 0.875 & 0.899 & 0.886 &  0.890 \\ \hline
& \multicolumn{6}{c|}{AUPRC}\\ \hline
Averaging     & 0.320 & 0.429 & 0.262 & 0.478 & 0.443 & 0.412 \\
Full method   &  &  &  & & &\\
PC & 0.074 & 0.218 & 0.082 & 0.165  & 0.193 & 0.135 \\
GTE & 0.094 & 0.211 & 0.081 & 0.165 & 0.210 & 0.144\\
GENIE3 & 0.128 & 0.261 & 0.108 & 0.293 & 0.256 & 0.224\\ \hline
\end{tabular}
\caption{Performance (top: AUROC, bottom: AUPRC) on specific datasets with different methods.}
\label{tab:results_appendix}
\end{table}
